Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-31 R0V0.tex
Changes regarding the maximum number of nodes simulated in Wolfram's computer

\mypara In the remainder of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara When $N\geq6$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

>>>>

\mypara In the remainder of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 32GB RAM, Ubuntu and on Matlab 2015b

@@

\mypara When $N>8$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}
